### 2018-04-10 latex/icpp18/experiments.tex
minor
partitioning done

\subsection {Effect of partitioning strategies}
In \cref{fig:nnzsweepcomm}, our first observation is that all partitionings except \krfaun yield comparable results in terms of communication, while there is some variation  in the computation times provided in \cref{fig:nnzsweepcomp}.
\krcun gives similar k

From the Figure \ref{fig:nnzsweepcomm},  it is evident that checkerboard partitioning with point-to-point
communication is approximately 4x faster over the 2D partition with collective communication. In the case of
computation, from Figure \ref{fig:nnzsweepcomp}, we can observe that in the case of denser matrices
with higher edge factors, the load imbalance in 2D is becoming more evident over the checkerboard partition. 
Thus checker board with point-to-point communicates less and has better load balance over 2D partition
with collective communication. These advantages  give scope for the checkerboard partition with point-to-point scale
to higher number of nodes.

@@

\begin{table}
\begin{center}
\caption{Load balance and communication statistics for 256-way partitioning.\label{tab:loadcomm}}
\vspace*{-1ex}
\begin{footnotesize}
  \begin{tabular}{ l | r | r | r | r | r }
%    \multirow{2}{*}{Partitioning} & \multicolumn{2}{|c|}{Nnz } & \multicolumn{2}{|c|}{Comp. Load} & \multicolumn{2}{|c|}{Comm. Vol.} & \multicolumn{2}{|c}{Num. Msg} \\ \cline{2-9}
    Partitioning & nz-ib  & row-ib      & col-ib     & com-max.      & com-avg \\ \hline
%    \multicolumn{6}{c}{\emph{Delicious}} \\ \hline
    fine-hp   & 547K      & 547K        & 1947K      & 1807K         & 199K      \\ \hline
    fine-lb   & 564K      & 547K        & 1849K      & 1737K         & 309K      \\ \hline
    fine-rd   & 550K      & 547K        & 2747K      & 2737K         & 1083K     \\ \hline
    medium-gd & 598K      & 547K        & 2353K      & 2214K         & 624K      \\ \hline
  \end{tabular}
  \end{footnotesize}
\end{center}
\vspace*{-1ex}
\end{table}

>>>>

\subsection {Effect of partitioning strategies}
In \cref{fig:nnzsweepcomm}, our first observation is that all partitionings except \krfaun yield comparable results in terms of communication, while there is some variation  in the computation times provided in \cref{fig:nnzsweepcomp}.
\krcun gives similar computation time to \krcr since matrix is randomly permuted.
\krcha yields slightly higher computation time and no notable improvement in the communication time, as it involves multi-constraint partitioning with too many constraints, which is a difficult partitioning problem that partitioners such as PaToH might not solve very effectively.
\krchb provides some advantage both in terms of computation and communication time, and this partitioning is feasible to compute as it involves hypergraph partitioning with only two constraints.

@@

\begin{table}
\begin{center}
\caption{Load balance and communication statistics for 256-way partitioning.\label{tab:loadcomm}}
\vspace*{-1ex}
\begin{footnotesize}
  \begin{tabular}{ l | r | r | r | r | r }
%    \multirow{2}{*}{Partitioning} & \multicolumn{2}{|c|}{Nnz } & \multicolumn{2}{|c|}{Comp. Load} & \multicolumn{2}{|c|}{Comm. Vol.} & \multicolumn{2}{|c}{Num. Msg} \\ \cline{2-9}
    Partitioning & nz-ib  & row-ib      & col-ib     & com-max.      & com-avg \\ \hline
%    \multicolumn{6}{c}{\emph{Delicious}} \\ \hline
    \krcun & 547K      & 547K        & 1947K      & 1807K         & 199K      \\ \hline
    \krcha & 564K      & 547K        & 1849K      & 1737K         & 309K      \\ \hline
    \krchb & 550K      & 547K        & 2747K      & 2737K         & 1083K     \\ \hline
    \krcr  & 598K      & 547K        & 2353K      & 2214K         & 624K      \\ \hline
    \krfh  & 598K      & 547K        & 2353K      & 2214K         & 624K      \\ \hline
  \end{tabular}
  \end{footnotesize}
\end{center}
\vspace*{-1ex}
\end{table}
